---
title: "G&S3-11"
author: "Rong Li"
date: "2021/2/10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load(knitr, ggplot2)
```


## Assignment Information

This assignment is due on Wednesday Feb 10.  Please submit your work by copying the github address for your work and please make sure that your code will run when it is downloaded (include an Rproj file and a README file).  

## Problem Background

Suppose that ordinary aspirin has been found effective against headaches 60 percent of the time, and that a drug company claims that its new aspirin with a special headache additive is more effective. We can test this claim as follows: $H_0 = 0.6$, $H_1 > 0.6$.  
We give the aspirin to n people to take when they have a headache. We want to find a number m, called the critical value for our experiment, such that we reject $H_0$ if at least m people are cured, and otherwise we accept it. There are t types of error.  

- Type 1 error: Assume that the $H_0 : p = 0.6$ is true, then if more than $m(m > \mu = np =0.6n)$ people are cured, we reject $H_0$.  
$$P(more\ than\ m\ people\ cured) = \alpha(0.6) = \sum_{m \leq k \leq n}b(n, 0.6, k)\ \hat =\ Type\ 1\ error$$
We want to choose m so as to make $\alpha(0.6)$ small, to reduce the likelihood of a type 1 error.  


- Type 2 error: Assume that the $H_1 : p > 0.6$ is true(the author choose $p = 0.8$ by casual), then if less than $m(m < \mu = np)$ people are cured, we reject $H_1$. We want type 2 error to be small either.  
$$P(less\ than\ m\ people\ cured) = 1 - \alpha(0.8) = 1 - \sum_{m \leq k \leq n}b(n, 0.8, k)\ \hat =\ \beta(0.8) \ =\ Type\ 2\ error$$
We want to choose m so as to make $\beta(0.8)$ small, to reduce the likelihood of a type 2 error.  

## Replicate Figure 3.7

In Figure 3.7, the author set n = 100, plot the $\alpha(p)$ for p ranging from 0.4 to 1. The left line is when m = 69 and right line is when m = 73.  

```{r}
PowerCurve <- function(p,m){
  sum <- 0
  for (i in m:100) sum = sum + dbinom(i, 100, p)
  return(sum)
}

x <- seq(.4, 1, .005)
y1 <- PowerCurve(x, 69)
y2 <- PowerCurve(x, 73)

ggplot() + 
  geom_line(mapping = aes(x = x, y = y1)) + 
  geom_line(mapping = aes(x = x, y = y2)) + 
  scale_x_continuous(limits = c(.4, 1), breaks = seq(.4, 1, .1), minor_breaks = NULL) + 
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, .1), minor_breaks = NULL) + 
  xlab("p") + 
  ylab("alpha(p)") + 
  geom_segment(aes(x = 0.6, y = 0.95, xend = 0.8, yend = 0.95)) + 
  geom_segment(aes(x = 0.6, y = 0.05, xend = 0.8, yend = 0.05)) + 
  geom_segment(aes(x = 0.6, y = 0.05, xend = 0.6, yend = 0.95)) + 
  geom_segment(aes(x = 0.8, y = 0.05, xend = 0.8, yend = 0.95))
```

## Explaination

In the problem background, we mentioned that we want to reduce the likelihood of type 1 and type 2 error. The author want our critical number m to make each of these undesirable cases less than 5
percent probable, which means $\alpha_{0.6}(m) < 0.05$ and $\beta_{0.8}(m) = 1- \alpha_{0.8}(m) < 0.05$.  
So that we need $\alpha_{0.6}(m) < 0.05$ and $\alpha_{0.8}(m) > 0.95$

- If we need $\alpha_{0.6}(m) < 0.05$, we first plot the $\alpha_{0.6}(m)$ vs. m.  

```{r, echo = FALSE}
y <- seq(1, 100)
for (i in 1:100) y[i] = PowerCurve(0.6, i)
ggplot(mapping = aes(x = 1:100, y = y)) + geom_line() + scale_x_continuous(limits = c(1, 100), breaks = seq(0, 100, 5)) + scale_y_continuous(breaks = seq(0, 1, 0.1)) + geom_abline(intercept = 0.05, slope = 0, col = 'blue') + xlab("m") + ylab("alpha0.6(m)") + labs(title = "The plot of alpha0.6(m) and m")
```

The cutpoint should lie between 65 and 70, we now print the value of $\alpha_{0.6}(m)$.  

```{r, echo = FALSE}
a = seq(1,6)
for (i in 65:70) a[i-64] = PowerCurve(0.6, i)
df = data.frame(m = 65:70, 'alpha0.6(m)' = a)
df
```

The cutpoint is 69. So, we need $m > 69$ to satisfy $\alpha_{0.6}(m) < 0.05$.  

- If we need $\alpha_{0.8}(m) > 0.95$, we first plot the $\alpha_{0.8}(m)$ vs. m.  

```{r, echo = FALSE}
y <- seq(1, 100)
for (i in 1:100) y[i] = PowerCurve(0.8, i)
ggplot(mapping = aes(x = 1:100, y = y)) + geom_line() + scale_x_continuous(limits = c(1, 100), breaks = seq(0, 100, 5)) + scale_y_continuous(breaks = seq(0, 1, 0.1)) + geom_abline(intercept = 0.95, slope = 0, col = 'blue') + xlab("m") + ylab("alpha0.8(m)") + labs(title = "The plot of alpha0.8(m) and m")
```

The cutpoint should lie between 70 and 75, we now print the value of $\alpha_{0.8}(m)$.  

```{r, echo = FALSE}
a = seq(1,6)
for (i in 70:75) a[i-69] = PowerCurve(0.8, i)
df = data.frame(m = 70:75, 'alpha0.8(m)' = a)
df
```

The cutpoint is 73. So, we need $m < 73$ to satisfy $\alpha_{0.8}(m) > 0.95$.  

In conclusion, we produce an explanation of the example showing how the authors reached their conclusion that the critical value should be between 69 and 73 people cured.





